### 2021-06-19 README.Rmd
added ff test logo to website

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

<!-- badges: start -->
<!-- badges: end -->

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
library(badger)
```

<img src="man/figures/logo.png" width="200" align="right"/>

@@

<!-- badges: start -->

<!-- `r badge_doi("10.1101/2020.11.19.389981", "yellow")` -->
[![R build status](https://github.com/nesscoder/fasano.franceschini.test/workflows/R-CMD-check/badge.svg)](https://github.com/nesscoder/fasano.franceschini.test/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")`
`r badge_code_size("nesscoder/fasano.franceschini.test")`

<!-- badges: end -->
